Recruiting Chapter

### 2020-11-30 manuscript.Rmd
updates to ego plots

plot_characteristic <- function(df, type, characteristics) {
  sub_df <- df %>% select(univ_name, characteristics) %>%
    gather(key, value, characteristics) %>%
    mutate(value = parse_number(value))

>>>>

plot_characteristic <- function(df, type, characteristic) {
  sub_df <- df %>% select(univ_name, characteristic) %>%
    gather(key, value, characteristic) %>%
    mutate(value = parse_number(value))
